---
title: 'qdap word_cor'
output: pdf_document
---

```{r, echo=FALSE}
library(knitr)
opts_knit$set(stop_on_error = FALSE)
```


You can't use qdap functions on a `Corpus` this way.  Typically qdap functions will work on a `Corpus` if you use them instid `apply_as_df`, however, in this cas the internals of `word_cor` is different enough that it can't just be put inside `apply_as_df` without me making some changes to the function.  Here I convert `alice` to a `data.frame` instead.

```{r}
pacman::p_install_gh("trinker/qdap")
pacman::p_load(tm, qdap)

alice <- readRDS("alice.rda")

class(alice)

dat <- sentSplit(as.data.frame(alice), "text")
head(with(dat, freq_terms(text)))
```

> My confusion seems to be with what constitutes a `grouping.var`:

I think this will help.  

```{r}
dat$id <- qdapTools::id(dat)
with(dat, word_cor(text, word="the", r = .01))
with(dat, word_cor(text, tot, word="the", r = .01))

with(dat, word_cor(text, word=c("she", "said", "the"), r = .3))
with(dat, word_cor(text, word=c("she", "said", "the"), r = NULL))

with(dat, word_cor(text, word=freq_terms(alice)[["WORD"]], r = .2))
with(dat, word_cor(text, word=freq_terms(alice)[["WORD"]], r = NULL))
```




